How geographic access to care shapes disease burden: the current impact of post-exposure prophylaxis and potential for expanded access to prevent human rabies deaths in Madagascar

### 2021-02-10 analysis/paper/manuscript.Rmd
fixing so no figs for sub & word output only

---
title: "How geographic access to care shapes disease burden: the current impact of post-exposure prophylaxis and potential for expanded access to prevent human rabies deaths in Madagascar"
author:
  - Malavika Rajeev:
      email: mrajeev@princeton.edu
      institute: [Princeton]
      correspondence: true
  - Hélène Guis:
      institute: [IPMepi, cirad, astre, fofifa]
      correspondence: false
  - Glenn Edosoa:
      institute: [OMS]
      correspondence: false
  - Chantal Hanitriniaina:
      institute: [UoA]
      correspondence: false
  - Anjasoa Randrianarijaona:
      institute: [IPMepi]
      correspondence: false
  - Reziky Tiandraza Mangahasimbola:
      institute: [IPMepi]
      correspondence: false
  - Fleur Hierink:
      institute: [Geneva]
      correspondence: false
  - Ravo Ramiandrasoa:
      institute: [IPMvacc]
      correspondence: false
  - José Nely:
      institute: [smeetn]
  - Jean-Michel Heraud:
      institute: [IPMviro]
      correspondence: false
  - Soa Fy Andriamandimby:
      institute: [IPMviro]
      correspondence: false
  - Laurence Baril:
      institute: [IC]
      correspondence: false
      equal_contributor: "yes"
  - C. Jessica E. Metcalf:
      institute: [Princeton]
      correspondence: false
      equal_contributor: "yes"
  - Katie Hampson:
      institute: [Glasgow]
      correspondence: false
      equal_contributor: "yes"
institute:
  - Princeton: Department of Ecology and Evolutionary Biology, Princeton University, Princeton, United States
  - IPMepi: Epidemiology and Clinical Research Unit, Institut Pasteur de Madagascar, Antananarivo, Madagascar
  - cirad: CIRAD, UMR ASTRE, Antananarivo, Madagascar
  - astre: ASTRE, Univ Montpellier, CIRAD, INRAE, Montpellier, France 
  - fofifa: FOFIFA-DRZVP, Antananarivo, Madagascar
  - OMS: Chargé des Maladies Tropicales Négligées, Organisation mondiale de la Santé Madagascar, Antananarivo, Madagascar
  - smeetn: Service contre les Maladies Endémo-épidémiques et Tropicales  Négligées, Ministère de la Santé Publique, Antananarivo, Madagascar
  - UoA: Mention Zoologie et Biodiversité Animale, Faculté des Sciences, Université d’Antananarivo, Antananarivo, Madagascar
  - Geneva: Institute of Global Health, Faculty of Medicine, University of Geneva, Geneva, Switzerland
  - IPMvacc: Vaccination Center, Institut Pasteur de Madagascar, Antananarivo, Madagascar
  - IPMviro: Virology Unit, Institut Pasteur de Madagascar, Antananarivo, Madagascar
  - IC: Institut Pasteur du Cambodge (previously Epidemiology and Clinical Research Unit at Institut Pasteur de Madagascar)
  - Glasgow: Boyd Orr Centre for Population and Ecosystem Health, Institute of Biodiversity, Animal Health and Comparative Medicine, University of Glasgow, Glasgow, UK
date: ""
nocite: '@*'
link-citations: no
output:
  bookdown::word_document2:
    pandoc_args:
      - --csl=format/plos-neglected-tropical-diseases.csl
      - --lua-filter=format/scholarly-metadata.lua
      - --lua-filter=format/author-info-blocks.lua
      - --lua-filter=format/pagebreak.lua
      - --lua-filter=format/multiple-bibliographies.lua
      - --reference-doc=format/reference_main.docx
  bookdown::html_document2:
    toc: true
    toc_float: true
    number_sections: no
    pandoc_args:
      - --csl=format/plos-neglected-tropical-diseases.csl
      - --lua-filter=format/scholarly-metadata.lua
      - --lua-filter=format/author-info-blocks.lua
      - --lua-filter=format/pagebreak.lua
      - --lua-filter=format/multiple-bibliographies.lua
keywords: "canine rabies, post-exposure prophylaxis, Gavi, Zero by 30, access to care"
#bibliography: ["bib/refs_all.bib", "bib/refs_pkgs.bib", "bib/refs_supextra.bib"]
bibliography_main: ["bib/refs_all.bib"]
bibliography_supp: ["bib/refs_pkgs.bib"]
bibliography_supextra: ["bib/refs_supextra.bib"]
---

@@

no_figs <- FALSE
if(no_figs) include_graphics <- function(x, ...) { return(invisible(NULL)) }
```

>>>>

---
title: "How geographic access to care shapes disease burden: the current impact of post-exposure prophylaxis and potential for expanded access to prevent human rabies deaths in Madagascar"
author:
  - Malavika Rajeev:
      email: mrajeev@princeton.edu
      institute: [Princeton]
      correspondence: true
  - Hélène Guis:
      institute: [IPMepi, cirad, astre, fofifa]
      correspondence: false
  - Glenn Edosoa:
      institute: [OMS]
      correspondence: false
  - Chantal Hanitriniaina:
      institute: [UoA]
      correspondence: false
  - Anjasoa Randrianarijaona:
      institute: [IPMepi]
      correspondence: false
  - Reziky Tiandraza Mangahasimbola:
      institute: [IPMepi]
      correspondence: false
  - Fleur Hierink:
      institute: [Geneva]
      correspondence: false
  - Ravo Ramiandrasoa:
      institute: [IPMvacc]
      correspondence: false
  - José Nely:
      institute: [smeetn]
  - Jean-Michel Heraud:
      institute: [IPMviro]
      correspondence: false
  - Soa Fy Andriamandimby:
      institute: [IPMviro]
      correspondence: false
  - Laurence Baril:
      institute: [IC]
      correspondence: false
      equal_contributor: "yes"
  - C. Jessica E. Metcalf:
      institute: [Princeton]
      correspondence: false
      equal_contributor: "yes"
  - Katie Hampson:
      institute: [Glasgow]
      correspondence: false
      equal_contributor: "yes"
institute:
  - Princeton: Department of Ecology and Evolutionary Biology, Princeton University, Princeton, United States
  - IPMepi: Epidemiology and Clinical Research Unit, Institut Pasteur de Madagascar, Antananarivo, Madagascar
  - cirad: CIRAD, UMR ASTRE, Antananarivo, Madagascar
  - astre: ASTRE, Univ Montpellier, CIRAD, INRAE, Montpellier, France 
  - fofifa: FOFIFA-DRZVP, Antananarivo, Madagascar
  - OMS: Chargé des Maladies Tropicales Négligées, Organisation mondiale de la Santé Madagascar, Antananarivo, Madagascar
  - smeetn: Service contre les Maladies Endémo-épidémiques et Tropicales  Négligées, Ministère de la Santé Publique, Antananarivo, Madagascar
  - UoA: Mention Zoologie et Biodiversité Animale, Faculté des Sciences, Université d’Antananarivo, Antananarivo, Madagascar
  - Geneva: Institute of Global Health, Faculty of Medicine, University of Geneva, Geneva, Switzerland
  - IPMvacc: Vaccination Center, Institut Pasteur de Madagascar, Antananarivo, Madagascar
  - IPMviro: Virology Unit, Institut Pasteur de Madagascar, Antananarivo, Madagascar
  - IC: Institut Pasteur du Cambodge (previously Epidemiology and Clinical Research Unit at Institut Pasteur de Madagascar)
  - Glasgow: Boyd Orr Centre for Population and Ecosystem Health, Institute of Biodiversity, Animal Health and Comparative Medicine, University of Glasgow, Glasgow, UK
date: ""
nocite: '@*'
link-citations: no
params:
  nofig: FALSE
output:
  bookdown::word_document2:
    pandoc_args:
      - --csl=format/plos-neglected-tropical-diseases.csl
      - --lua-filter=format/scholarly-metadata.lua
      - --lua-filter=format/author-info-blocks.lua
      - --lua-filter=format/pagebreak.lua
      - --lua-filter=format/multiple-bibliographies.lua
      - --reference-doc=format/reference_main.docx
  bookdown::html_document2:
    toc: true
    toc_float: true
    number_sections: no
    pandoc_args:
      - --csl=format/plos-neglected-tropical-diseases.csl
      - --lua-filter=format/scholarly-metadata.lua
      - --lua-filter=format/author-info-blocks.lua
      - --lua-filter=format/pagebreak.lua
      - --lua-filter=format/multiple-bibliographies.lua
keywords: "canine rabies, post-exposure prophylaxis, Gavi, Zero by 30, access to care"
#bibliography: ["bib/refs_all.bib", "bib/refs_pkgs.bib", "bib/refs_supextra.bib"]
bibliography_main: ["bib/refs_all.bib"]
bibliography_supp: ["bib/refs_pkgs.bib"]
bibliography_supextra: ["bib/refs_supextra.bib"]
---

@@

no_figs <- params$nofig
if(no_figs) include_graphics <- function(x, ...) { return(invisible(NULL)) }
```
